---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DemoPreTurningPointsCOVID19

<!-- badges: start -->
<!-- badges: end -->

This R package aims to implementing the computational framework in the paper *[Tracking and forecasting milepost moments of the epidemic in the early outbreak framework and applications to the COVID-19](https://www.medrxiv.org/content/10.1101/2020.03.21.20040139v1.full.pdf+html)* based entirly on the [Vicky-Zh's work](https://github.com/Vicky-Zh/Tracking_and_forecasting_milepost_moments_of_COVID-19.git).

## Installation

You can install it as a binary package or source package.

Install from binary:

- Download Binary File **DemoPreTurningPointsCOVID19_1.0.0.zip
** from https://github.com/YuanchenZhu2020/DemoPreTurningPointsCOVID19/releases/tag/Version_1.0.0
- Get the path of this binary file: `pkgfilepath`
- Install packages in R: `install.packages(pkgfilepath, repos = NULL)`


Install from source code:

- download and install **RTools**. (Mirrors:  https://mirrors.tuna.tsinghua.edu.cn/CRAN/bin/windows/Rtools/)
- install **devtools** in R `install.packages("devtools")`
- install packages in R `devtools::install_github("YuanchenZhu2020/DemoPreTurningPointsCOVID19")`


``` r
# install as a binary package.
# 1. download binary package to your PC
# 2. get the path of package file
install.packages(pkgfilepath, repos = NULL)

# install as a source code package (requires RTools)
# install.packages("devtools")
devtools::install_github("YuanchenZhu2020/DemoPreTurningPointsCOVID19")
```

## Usage

Function List:

  - get_indicators
  - calc_velocity
  - get_future_indicators
  - corr_removed_rate
  - get_milepost
  - prediction
  - period_predict
  - prediction

Dataset List:

  - COVID19_CN

If you want to see details of each function or dataset, use `help(name)`. Or you can download the [referance manual](https://github.com/YuanchenZhu2020/DemoPreTurningPointsCOVID19/releases/tag/Version_1.0.0).

## Example


```{r example}
library(DemoPreTurningPointsCOVID19)
# single begining time
single_result <- prediction(COVID19_CN, M = 5, Beginning_Time = "2020-01-29")

# multiple begining time
period_result <- period_predict(COVID19_CN, M = 5, Beginning_Time = "2020-01-29", period = 32)
```
